master thesis

### 2018-01-31 Paper - Latex/Paper - Skizze - v1.tex
Paper - Methods - GloBI + Countings

@@

    %---------------------------------------------------------------------------------------------------
    \subsection{countings}
      Some simple countings...\\
      nr of parasites, free-living and unknown nodes ... from whole tree, subtrees...

>>>>

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Get data}
    %---------------------------------------------------------------------------------------------------
    \subsection{GloBI}
      For tagging our leave nodes, we use the GloBI (Global Biotic Interactions) database. This database 
        consists of entries of the form: species A interacts with B. \\
      We appointed some interactions, where we know from the biological perspective that the species 
      source or target has to be a parasite or a free-living species. These are the following:
      \begin{lstlisting}
        freeliving_source = ["parasiteOf", "pathogenOf"]
        freeliving_target = ["hasParasite", "hasPathogen"]
        parasite_source = ["preysOn", "eats", "flowersVisitedBy", "hasPathogen", "pollinatedBy", "hasParasite", "hostOf"]
        parasite_target = ["preyedUponBy", "parasiteOf", "visitsFlowersOf", "pathogenOf", "hasHost"]
      \end{lstlisting}
      We build two lists: parasites and free-livings, and add the source or targets of an interaction
        to these. \\
      \todo{klar? Oder Beispiel bringen? (Katze isst Maus -> Katze ist Freilebend)} \\
      % For every interaction from these lists, we get one or two species for our parasite or 
      %   free-living lists.
      \todo{ott id hier erwähnen?} \\
      \todo{einige spezies nicht mit einbezogen, da sie keine OTT id haben, hier könnte man noch verbessern (future work)}
      \todo{You can find all interaction types here: https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .}

    %---------------------------------------------------------------------------------------------------
    \subsection{OTL}
      \todo{Open Tree of Life}

@@

    %---------------------------------------------------------------------------------------------------
    \subsection{Countings}
      Some simple countings...\\
      nr of parasites, free-living and unknown nodes ... from whole tree, subtrees...
      \begin{center}
        \begin{tabular}{ | l | p{3cm} | }
          \hline
          Name & Number of \\
          \hline \hline
          interactions & 5346414 \\ \hline
          freeliving species & 48875 (distinct) \\ \hline
          parasite species &  64125 (distinct) \\ \hline
          unused possible species & 2126 (source), 2144439 (target) \\
          % number of freelivings: 509595
          % number of freelivings: 45881 (distinct)
          % number of parasites: 3438001
          % number of parasites: 63532 (distinct)
          % number of SAME_AS: 16012
          % number of SAME_AS: 5667 (distinct)
          \hline  
        \end{tabular}
      \end{center}
